Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-16 prop_iop.tex
prop_iop.tex Updating here and there...

In informal terms, this result states that although measurements done
with limited resources and poor precision may not uniquely identify
the true state of the system, there is always at least one system
that is consistent with the measurements. Surprisingly, we discovered
a counterexample to this statement in the quantum case, and have the
following theorem.

@@

The possibility that a quantum interval-valued probability measure
has an empty core departs from the classical cases. In order to understand
its meaning, we will first study how to recover the non-empty core
by adding conditions. Then, we will consider having an empty core
as an legitimate result, and understand its consequence.

@@

One possibility is that the definition of quantum convexity is too
weak to guarantee an convex quantum interval-valued probability measure
has an non-empty core. However, the product of non-commuting projectors
is not a projector so that equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
cannot be meaningful when $P_{0}$ and $P_{1}$ are non-commuting.

Classically, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
is a special case of 
\begin{equation}
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
\end{equation}
If a classical interval-valued probability measure~$\bar{\mu}$ satisfies
equation~(\ref{eq:Dempster-Shafer-game}) for all set of event~$\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$,
then the left-end point of $\bar{\mu}$ is called a Dempster-Shafer
belief function. Equation~(\ref{eq:Dempster-Shafer-game}) could
be extended to the quantum case, and consider a quantum interval-valued
probability measure satisfying 
\begin{equation}
\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
\end{equation}
for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
However, example~\ref{ex:three-dimensional-three-value} satisfies
equation~(\ref{eq:Dempster-Shafer-game-quantum}) as well. In another
word, this kind of conditions cannot eliminate the situation of empty
core.

>>>>

In informal terms, this result states that although measurements done
with limited resources and poor precision may not uniquely identify
the true state of the system, there is always at least one system
that is consistent with the measurements. Surprisingly, we discovered
a counterexample to this statement in the quantum case, and have:

@@

The possibility that a quantum interval-valued probability measure
has an empty core departs from the classical case. To understand the
meaning of it, we will first study how to recover the non-empty core
with extra conditions. Then, we will consider having an empty core
as an legitimate result, and understand its consequence.

@@

One possibility is that the definition of quantum convexity is too
weak to guarantee a convex quantum interval-valued probability measure
having a non-empty core. On one hand, the product of non-commuting
projectors is not a projector so equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
is unlikely to extended to non-commuting projectors~$P_{0}$ and
$P_{1}$. On the other hand, we haven't found a way to guarantee a
non-empty core if we only strength the condition on commuting projectors
as well. For example, classically, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
is a special case of 
\begin{equation}
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
\end{equation}
If a classical interval-valued probability measure~$\bar{\mu}$ satisfies
equation~(\ref{eq:Dempster-Shafer-game}) for all set of event~$\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$,
then the left-end point of $\bar{\mu}$ is called a Dempster-Shafer
belief function. Equation~(\ref{eq:Dempster-Shafer-game}) could
be extended to the quantum case. However, example~\ref{ex:three-dimensional-three-value}
also satisfies the corresponding condition for quantum interval-valued
probability measure: 
\begin{equation}
\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
\end{equation}
for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
In another word, this kind of conditions cannot eliminate the situation
of empty core.
